Concurrent Programming with Harmony

### 2020-07-25 book/paper.tex
Fixed question
Updating book

\section*{Exercises}
\begin{problems}
\item Write a synchronization module using your own implementation of \texttt{Lock}
(for example, using Peterson's algorithm or using \texttt{swap}).
\item
Run \autoref{fig:incfixed} using (1) \texttt{synch}, (2), \texttt{synchS},
and (3) your own module.  Report how many states were explored by Harmony for each
version of the module.
\item \label{ex:trylock} Implement \texttt{trylock}(\textit{lk}) as an additional
interface to the \texttt{synch} and \texttt{synchS} modules.
This interface is like \texttt{lock}(\textit{lk}) but never blocks.  It
returns \texttt{True} if the lock was available (and now acquired) or \texttt{False}
if the lock was already taken.
\end{problems}

@@

{\small
\begin{tabular}{|l|l|}
\hline
\texttt{$e$ == $e$}, \texttt{$e$ != $e$} & two Harmony values of the same type \\
\hline
\texttt{$e$ < $e$, $e$ <= $e$} & any two Harmony values \\
\hline
\texttt{$e$ > $e$, $e$ >= $e$} & any two Harmony values \\
\hline
\texttt{$e$ and $e$ and ...} & two or more booleans \\
\hline
\texttt{$e$ or $e$ or ...} & two or more booleans \\
\hline
\texttt{not $e$} & a boolean \\
\hline
\texttt{-$e$, \string~$e$} & an integer \\
\hline
\texttt{$e$ + $e$ + ...} & two or more integers, tuples, or lists \\
\hline
\texttt{$e$ * $e$ * ...} & two or more integers \\
\hline
\texttt{$e$ - $e$} & two integers or sets \\
\hline
\texttt{$e$ \& $e$ \& ...} & two or more integers or sets \\
\hline
\texttt{$e$ | $e$ | ...} & two or more integers or sets \\
\hline
\texttt{$e$ \string^ $e$ \string^ ...} & two or more integers or sets \\
\hline
\texttt{$e$ / $e$, $e$ // $e$} & two integers (integer division) \\
\hline
\texttt{$e$ \% $e$, $e$ mod $e$} & two integers (division remainder) \\
\hline
\texttt{$e$ ** $e$, $e << e$, $e >> e$} & two integers \\
\hline
\texttt{$\{ e..e \}$} & two integers \\
\hline
\texttt{$e$ [not] in $e$} & first is any Harmony value, second is set \\
\hline
\texttt{$e$ if $e$ else $e$} & middle $e$ must be a boolean \\
\hline
\texttt{!{}$e$} & an address \\
\hline
\texttt{choose $e$} & a set \\
\hline
\texttt{min $e$, max $e$} & a set \\
\hline
\texttt{cardinality $e$} & a set \\
\hline
\texttt{keys $e$, len $e$} & a dictionary (includes tuple or list) \\
\hline
\texttt{bagsize $e$} & a bag \\
\hline
\texttt{atLabel $e$} & atom (corresponding to a label) \\
\hline
\texttt{nametag $e$} & $e$ must be \texttt{()} \\
\hline
\texttt{processes $e$} & $e$ must be \texttt{()} \\
\hline
\texttt{setintlevel} \textit{e} & \textit{e} is a boolean \\
\hline
\texttt{stop} \textit{lv} & \textit{lv} is an lvalue \\
\hline
\texttt{?}\textit{lv} & \textit{lv} is an lvalue \\
\hline
\end{tabular}
}
\vspace{1em}

@@

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
\textit{lv} = $e$ & \textit{lv} is an lvalue and $e$ is an expression\\
\hline
\textit{lv} \texttt{[op]=} $e$ & \texttt{op} is one of \texttt{+}, \texttt{-}, \texttt{*}, \texttt{/}, 
\texttt{and}, and \texttt{or}\\
\hline
\texttt{pass} & do nothing\\
\hline
\texttt{del} \textit{lv} & delete\\
\hline
\texttt{assert $b$ [, $e$]} & $b$ is a boolean.  Optionally report value of expression $e$\\
\hline
\texttt{const v = $e$} & \texttt{v} is an identifier, $e$ is a constant expression\\
\hline
\texttt{def m($v$, ...): S} & \texttt{m} and \texttt{v} are identifiers, \texttt{S} a list of statements\\
\hline
\texttt{let $v$ = $e$ [let ...]: S} & $v$ is an identifier, $e$ is an expression, \texttt{S} a list of statements\\
\hline
\texttt{if $b$: S} & $b$ is a boolean, \texttt{S} a list of statements\\
\hline
\texttt{while $b$: S} & $b$ is a boolean, \texttt{S} a list of statements\\
\hline
\texttt{for $v$ in $e$: S} & $v$ is an identifier, $e$ is a set,
                            \texttt{S} a list of statements\\
\hline
\texttt{atomic: S} & \texttt{S} a list of statements\\
\hline
\texttt{spawn m $e$ [, $t$]} & \texttt{m} is a method,
$e$ is an expression, $t$ is a tag (an expression) \\
\hline
\texttt{trap m $e$} & \texttt{m} is a method and $e$ is an expression \\
\hline
\texttt{go $c$ $e$} & $c$ is a context, $e$ is an expression \\
\hline
\texttt{import m} & \texttt{m} identifies a module \\
\hline
\end{tabular}
\vspace{1em}

>>>>

\section*{Exercises}
\begin{problems}
\item Write a new synchronization module, similar to \autoref{fig:spinlocks}, but using
atomic swap.
\item
Run \autoref{fig:incfixed} using (1) \texttt{synch}, (2), \texttt{synchS},
and (3) your own module.  Report how many states were explored by Harmony for each
version of the module.
\item \label{ex:trylock} Implement \texttt{trylock}(\textit{lk}) as an additional
interface to the \texttt{synch} and \texttt{synchS} modules.
This interface is like \texttt{lock}(\textit{lk}) but never blocks.  It
returns \texttt{True} if the lock was available (and now acquired) or \texttt{False}
if the lock was already taken.
\end{problems}

@@

{\small
\begin{tabular}{|l|l|}
\hline
\texttt{$e$ == $e$}, \texttt{$e$ != $e$} & two Harmony values of the same type \\
\hline
\texttt{$e$ < $e$, $e$ <= $e$} & any two Harmony values \\
\hline
\texttt{$e$ > $e$, $e$ >= $e$} & any two Harmony values \\
\hline
\texttt{$e$ and $e$ and ...} & two or more booleans \\
\hline
\texttt{$e$ or $e$ or ...} & two or more booleans \\
\hline
\texttt{not $e$} & a boolean \\
\hline
\texttt{-$e$, \string~$e$} & an integer \\
\hline
\texttt{$e$ + $e$ + ...} & two or more integers, tuples, or lists \\
\hline
\texttt{$e$ * $e$ * ...} & two or more integers \\
\hline
\texttt{$e$ - $e$} & two integers or sets \\
\hline
\texttt{$e$ \& $e$ \& ...} & two or more integers or sets \\
\hline
\texttt{$e$ | $e$ | ...} & two or more integers or sets \\
\hline
\texttt{$e$ \string^ $e$ \string^ ...} & two or more integers or sets \\
\hline
\texttt{$e$ / $e$, $e$ // $e$} & two integers (integer division) \\
\hline
\texttt{$e$ \% $e$, $e$ mod $e$} & two integers (division remainder) \\
\hline
\texttt{$e$ ** $e$, $e << e$, $e >> e$} & two integers \\
\hline
\texttt{$\{ e..e \}$} & two integers \\
\hline
\texttt{$e$ [not] in $e$} & first is any Harmony value, second is set \\
\hline
\texttt{$e$ if $e$ else $e$} & middle $e$ must be a boolean \\
\hline
\texttt{!{}$e$} & an address \\
\hline
\texttt{choose $e$} & a set \\
\hline
\texttt{min $e$, max $e$} & a set \\
\hline
\texttt{cardinality $e$} & a set \\
\hline
\texttt{keys $e$, len $e$} & a dictionary (includes tuple or list) \\
\hline
\texttt{bagsize $e$} & a bag \\
\hline
\texttt{atLabel $e$} & atom (corresponding to a label) \\
\hline
\texttt{nametag $e$} & $e$ must be \texttt{()} \\
\hline
\texttt{processes $e$} & $e$ must be \texttt{()} \\
\hline
\texttt{setintlevel} \textit{e} & \textit{e} is a boolean \\
\hline
\texttt{stop} \textit{lv} & \textit{lv} is an lvalue \\
\hline
\texttt{?}\textit{lv} & \textit{lv} is an lvalue \\
\hline
\texttt{lambda $b$: $e$ end} & $b$ is a bounded variable, $e$ an expression\\
\hline
\end{tabular}
}
\vspace{1em}

@@

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
\textit{lv} = $e$ & \textit{lv} is an lvalue and $e$ is an expression\\
\hline
\textit{lv} \texttt{[op]=} $e$ & \texttt{op} is one of \texttt{+}, \texttt{-}, \texttt{*}, \texttt{/}, 
\texttt{and}, and \texttt{or}\\
\hline
\texttt{pass} & do nothing\\
\hline
\texttt{del} \textit{lv} & delete\\
\hline
\texttt{assert $b$ [, $e$]} & $b$ is a boolean.  Optionally report value of expression $e$\\
\hline
\texttt{const b = $e$} & \texttt{b} is a bounded variable, $e$ is a constant expression\\
\hline
\texttt{def m $b$: S} & \texttt{m} is an identifier, $b$ a bounded variable, \texttt{S} a list of statements\\
\hline
\texttt{let $b$ = $e$ [let ...]: S} & $b$ is a bounded variable, $e$ is an expression, \texttt{S} a list of statements\\
\hline
\texttt{if $b$: S} & $b$ is a boolean, \texttt{S} a list of statements\\
\hline
\texttt{while $b$: S} & $b$ is a boolean, \texttt{S} a list of statements\\
\hline
\texttt{for $b$ in $e$: S} & $b$ is a bounded variable, $e$ is a set,
                            \texttt{S} a list of statements\\
\hline
\texttt{atomic: S} & \texttt{S} a list of statements\\
\hline
\texttt{spawn m $e$ [, $t$]} & \texttt{m} is a method,
$e$ is an expression, $t$ is a tag (an expression) \\
\hline
\texttt{trap m $e$} & \texttt{m} is a method and $e$ is an expression \\
\hline
\texttt{go $c$ $e$} & $c$ is a context, $e$ is an expression \\
\hline
\texttt{import m} & \texttt{m} identifies a module \\
\hline
\end{tabular}
\vspace{1em}
